Improving the Replicability of Psychological Science Through Pedagogy

### 2017-07-20 paper/paper.Rmd
Switch parts over to sentence-per-line for better diffs...
mcf tweaks

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct replications as part of their training. As a proof-of-concept for this idea, here we report a series of 11 pre-registered replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. Congruent with larger, more systematic efforts, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim. This work documents the challenges facing motivated students in reproducing previously published results on a first attempt. We describe the workflow and pedagogical methods that were used in the class and discuss implications both for the adoption of this pedagogical model and for replication research more broadly."

@@

<!-- The problem, a solution, and the current lack of evidence for it -->
Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued for publication [@makel2012] or in metrics of research productivity [@koole2012]. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.

<!-- The kind of evidence we're going to provide -->
In the current article, we address the practical barriers faced by instructors planning to incorporate replications into their courses. As a concrete guide for other instructors, we report the pedagogical and methodological approach taken in our graduate-level experimental methods course. In this course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science* with rigorous instructor review at each major stage. The results of these replications represent a microcosm of larger replication efforts, providing insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

@@

<!-- The educational value of that evidence  -->
We also describe in detail our process for conducting replications as part of classroom pedagogy. Although mentorship in experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances. And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- more directly than open-ended projects, which require new conceptual development [see @frank2012 for extended argument].

<!-- Inspirational stuff and a call to join us... -->
There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise. Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole -- both scientific and educational -- would be considerable. To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/). In addition, all of our most recent lecture slides and materials are available on our course website at [http://psych254.stanford.edu](). We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.

@@

As described below, our procedure for individual project preregistrations was to register the analytic script with specific key hypothesis tests clearly marked. Individual project preregistration links are given at [osf.io/98ta4/wiki/](osf.io/98ta4/wiki/). Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper at [https://osf.io/rxz8m/](https://osf.io/rxz8m/).

@@

All replications were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction" and was conducted in accordance with the Declaration of Helsinki.

@@

RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper. CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned individual projects, programmed studies, collected data, analyzed data, and gave feedback on the paper.

@@

All projects were completed as part of a graduate-level methodology class. At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project. The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.  A schematic of our class timeline is shown in Figure 1.

@@

All study participants were recruited on Amazon Mechanical Turk (AMT). Individual sample sizes are given in Table \ref{tab:summary}. Each sample was recruited independently, using the same account but a different title. Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT. For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.

We determined sample sizes using a case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget (see below for discussion).^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study. In four cases, we powered the replication attempt to 80\% power based on post-hoc power calculations of the original effect sizes. In four cases, we used the original sample size. In one case, the original study was powered well above what would be required to find the effect of interest based on the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect. In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.

@@

Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, following the methods specified by the original authors as closely as possible.
Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available. 
For `r sum(project_plan$author_contact != "")` studies, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials). 
Responses were received in all but one case, all within a matter of days.

@@

In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants (see Fig. 1). In the second week of the course, students wrote a brief proposal selecting their replication targets, which were reviewed for feasibility and concreteness. After their selection was approved, students proceeded to write the methods section of the @osc2015 replication report template. This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template). At the same time, students worked on an experiment 'mock-up': a fully functional but unpolished outline of their experiment, potentially using placeholders for one or more unfinished elements of the design. Upon reviewing the completed methods and mockup, the teaching staff gave thorough feedback and suggested changes to be made before beginning any data collection.

Further reviews were coordinated with completion of two pilot samples. The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students). The goal of this pilot was to ensure that all needed data were being accurately logged and that analytic scripts for the confirmatory analyses functioned appropriately. After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script, analytic code, and resulting output.

@@

Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study. Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below). Despite this interpretive difficulty, we followed previous work and attempted to use a single statistical test as our target for replication planning and analysis.

@@

All of the 15 students in the class completed projects (two with extensions going beyond the class period). Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations, and materials to the final product. (In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review. We included this project in the final analysis.)

@@

Student group & \multicolumn{1}{p{2in}}{\raggedright General Undergraduate} & \multicolumn{1}{p{2in}}{\raggedright Advanced Undergraduate or Graduate} & \multicolumn{1}{p{2in}}{\raggedright Sophisticated Graduate} \\

@@

Group size & \multicolumn{1}{p{2in}}{\raggedright Full class / medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\

Project selection & \multicolumn{1}{p{2in}}{\raggedright Single class replication or small curated list} & \multicolumn{1}{p{2in}}{\raggedright Curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection} \\

Subject population & \multicolumn{1}{p{2in}}{\raggedright University or classroom participant pool} & \multicolumn{1}{p{2in}}{\raggedright In-person or online convenience sample} & \multicolumn{1}{p{2in}}{\raggedright Targeted sampling of original populations} \\

Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use GUI tools / instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key open-source tool (e.g., R)} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key open-source tools} \\

Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor (drafted by students)} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students (with instructor review)} \\

Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default (subject to discussion)} \\

@@

In our class, students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility. We encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design. This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at lower levels. For example, in a large undergraduate class it may be logistically simpler for the instructors to choose a small set of replication projects that students can select from. This step would both give instructors a greater degree of familiarity with the literature and allow for the development of more scaffolding with respect to the development of experimental materials. A mid-level course might split the difference between these two models, providing students with a broader -- but still curated -- list of potential projects.

@@

We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.^[Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge. We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses due to failures to distinguish between related experimental paradigms. In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).] We used AMT to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills. Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers. Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some of our results. Other classes many find participant pools or recruitment of community samples more feasible and appropriate.

@@

All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document. This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors (@nuijten2015), given that errors are often introduced by transferring results between statistics and word-processing software packages.].

Some of these tools can feel inaccessible or intimidating to students with a more limited programming background. Indeed, our students, who came from a variety of disciplinary backgrounds, typically have relatively little experience with web-based empirical studies or literate, reproducible data analysis. Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out an independent project (with support from their peers and the course staff). Our experience suggests that it is possible to convey key concepts in sufficient depth that students can learn to use a broad range of open and reproducible tools for their projects, even if mastery will require further experience.

@@

Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015]. Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013]. But -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered. In general, samples for course projects will be limited by the available resources. For all replication research of the type advocated here, achieving high power for a smaller number of studies, perhaps conducted by groups, is preferable to conducting more lower-power studies, because results are much more likely to make a contribution to the replication literature (as well as to be interpretable by students). Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.

@@

Ethical review standards vary across countries and are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects. First, instructors may first be concerned that ethics approval is not possible within the time constraints of the class. To mitigate this issue, we suggest contacting your ethics body well in advance of the class to determine whether to create a standard protocol that encompasses all replications that will be conducted (as we did), or to determine a timeline for submitting individual protocols very early in the course. Both types of protocol will be simplified if the study or pool of studies to be replicated is pre-selected by instructors. Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters. We recommend building training around ethical issues into the syllabus of replication-based classes. This practice is both positive for students and mitigates potential ethics approval concerns via the inclusion of explicit training.

@@

All reported results are from pre-registered, confirmatory analyses.^[In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).]

@@

Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies. We coded projects independently on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), and then discussed our ratings and made adjustments (without coming to full consensus). The mean rating was `r round(mean(d$fidelity), digits = 2)` (range: `r round(min(d$fidelity), digits = 2)` -- `r round(max(d$fidelity), digits = 2)`). Several studies were essentially identical to the originals, but there was a group of others that included differences in population, number of trials, or method that might plausibly have had an effect on the results.

@@

After data analysis, for each replication, the student carrying out each study and the instructors all gave independent "replication ratings" to assess the subjective success of the replication. Our three-point rating system was based on the theoretical support for the original finding, "None" (no support; 0\%), "Partial" (some support; 50\%), and "Full" (replication consistent with original interpretation; 100\%). We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r 100 * round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)`\% and `r 100 * round(mean(d$replicated_student, na.rm=TRUE), digits = 2)`\% respectively.

@@

We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level. Only `r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value. The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.

@@

However, our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear. For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials. In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample. And in some, differences of population would mean that followups would require further stimulus or task adaptation. More generally, we believe that our work here underscores the importance of iterated replication for pinpointing empirical effects and refining theories [see e.g., @lewis2016 for an example of this strategy and some discussion].

>>>>

abstract: 
    "Replications are important to science, but who will do them? One proposal is that students can conduct replications as part of their training. As a proof-of-concept for this idea, here we report a series of 11 pre-registered replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course. Congruent with larger, more systematic efforts, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim. This work documents the challenges facing motivated students as they attempt to replicate previously published results on a first attempt. We describe the workflow and pedagogical methods that were used in the class and discuss implications both for the adoption of this pedagogical model and for replication research more broadly."

@@

<!-- The problem, a solution, and the current lack of evidence for it -->
Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. 
Yet under the current incentive structure for science, replication is not typically valued for publication in top journals [@makel2012] or in metrics of research productivity [@koole2012]. 
One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. 
Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports and individual projects [e.g., @phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.

<!-- The kind of evidence we're going to provide -->
In the current article, we describe the pedagogical and methodological approach to replication research taken in our graduate-level experimental methods course and address the practical barriers faced by instructors planning to incorporate replications into their courses.
In our course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science* with rigorous instructor review at each major stage. 
The results of these replications are a microcosm of larger replication efforts, providing insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

@@

<!-- The educational value of that evidence  -->
We also describe in detail our process for conducting replications as part of classroom pedagogy. 
Although mentorship in experimental methods is an important part of the standard advising relationship in psychology, the classroom context allows for the elucidation of general principles of good research and discussion of how they can be modified to fit specific instances. 
And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- more directly than open-ended projects, which require new conceptual development [see @frank2012 for extended argument].

<!-- Inspirational stuff and a call to join us... -->
There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise. 
Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole -- both scientific and educational -- would be considerable. 
To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/). 
In addition, all of our most recent lecture slides and materials are available on our course website at [http://psych254.stanford.edu](). 
We hope that others will share and reuse our materials as they consider how best to design a course customized to their aims and context.

@@

As described below, our procedure for individual project preregistrations was to register the analytic script with specific key hypothesis tests clearly marked. 
Individual project preregistration links are given at [https://osf.io/98ta4/wiki/](osf.io/98ta4/wiki/). 
Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper at [https://osf.io/rxz8m/](https://osf.io/rxz8m/).

@@

All replications were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction" and were conducted in accordance with the Declaration of Helsinki.

@@

RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper. MCF designed the course.
CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned individual projects, programmed studies, collected data, analyzed data, and gave feedback on the paper.

@@

All projects were completed as part of a graduate-level methodology class. 
At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project. 
The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup. 
A schematic of our class timeline is shown in Fig. 1.

@@

All study participants were recruited on Amazon Mechanical Turk (AMT). 
Individual sample sizes are given in Table \ref{tab:summary}.
Each sample was recruited independently, using the same AMT account but a different task title.
Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT. 
For the other studies in our sample, demographic differences between the original sample and the AMT sample (in terms of age, sex, socio-economic status, and in some cases, national origin) are a factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.^[Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge. We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses due to failures to distinguish between related experimental paradigms. In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).]

We determined sample sizes using a case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget (see below for discussion).^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions [@salehi2015].] 
To ensure they still achieved the desired criterion if some participants skipped through or did not complete the study, experimenters recruited 5% more participants than specified by their criterion. 
In four cases, we powered the replication attempt to 80\% power based on post-hoc power calculations of the original effect sizes. 
In four cases, we used the original sample size. 
In one case, the original study was powered well above what would be required to find the effect of interest based on the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power to detect that effect. 
In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). 
In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.

@@

Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, otherwise following the methods specified by the original authors as closely as possible.
Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available. 
For `r sum(project_plan$author_contact != "")` studies, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials). 
Responses were received in all but one case, all within a matter of days.

@@

In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants (see Fig. 1). 
In the second week of the course, students wrote a brief proposal selecting their replication targets, which were reviewed for feasibility and concreteness. 
After their selection was approved, students proceeded to write the methods section of the @osc2015 replication report template. 
This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template). 
At the same time, students worked on an experiment "mock-up": a fully functional but unpolished outline of their experiment, potentially using placeholders for one or more unfinished elements of the design. 
Upon reviewing the completed methods and mockup, the teaching staff gave thorough feedback and suggested changes to be made before beginning any data collection.

For each project, further reviews were triggered by the completion of two pilot samples. The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students). The goal of this pilot was to ensure that all needed data were being accurately logged and that analytic scripts for the confirmatory analyses functioned appropriately. After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script, analytic code, and resulting output.

@@

Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test for each study. Usually a substantial number of statistical tests were conducted, often within one or several ANOVA or regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below). Despite this interpretive difficulty, we followed previous work and attempted to use a single statistical test as our target for replication planning and analysis.

@@

All of the 15 students in the class completed projects (two with extensions going beyond the class period). Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[These students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations, and materials to the final product. (In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review. We included this project in the final analysis.)

@@

Student group & \multicolumn{1}{p{2in}}{\raggedright Mid-level undergraduates} & \multicolumn{1}{p{2in}}{\raggedright Advanced undergraduates or graduate students} & \multicolumn{1}{p{2in}}{\raggedright Advanced graduate students} \\

@@

Project group size & \multicolumn{1}{p{2in}}{\raggedright Full class or medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individuals} \\

Project selection & \multicolumn{1}{p{2in}}{\raggedright Full class replication or choose from small curated list} & \multicolumn{1}{p{2in}}{\raggedright Choose from curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection or meta-science sampling frame} \\

Subject population & \multicolumn{1}{p{2in}}{\raggedright In-person convenience samples} & \multicolumn{1}{p{2in}}{\raggedright University pool or AMT} & \multicolumn{1}{p{2in}}{\raggedright AMT or targeted sampling of original populations} \\

Workflow tools & \multicolumn{1}{p{2in}}{\raggedright GUI tools, instructors code studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key coding-based tool, GUI tools otherwise} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key coding tools} \\

Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration drafted by students} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students with instructor review} \\

Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default, subject to review} \\

@@

In our class, students selected projects based on interest, and we encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design. This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at lower levels. For example, in a large undergraduate class it may be logistically simpler for the instructors to choose a small set of replication projects that students can select from, or perhaps even pool resources and collect multiple datasets for a single project. Limiting the set of projects both gives instructors a greater degree of familiarity with the relevant literature and allows for the development of more scaffolding of experimental materials. A mid-level course might split the difference between these two models, providing students with a broader -- but still curated -- list of potential projects.

@@

We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies. We used AMT to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills. Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers. Other classes many find using university participant pools or recruitment of community samples more feasible and appropriate.

@@

All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document. This method of writing allows students to share a single compiled document with instructors via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].

Some of these tools can feel inaccessible or intimidating to students with a more limited programming background. Indeed, our students came from a variety of disciplinary backgrounds; many had relatively little experience with web-based empirical studies or literate, reproducible data analysis. Yet by the end of the course, all gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out an independent project with support from their peers and the course staff. Our experience suggests that it is possible to convey key concepts in sufficient depth that students can learn to use a broad range of open and reproducible tools for their projects, even if mastery will require further experience.

@@

Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015]. Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013]. But -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered. Samples for course projects will be limited by the available resources, but for replication research of the type advocated here, achieving high power for a smaller number of studies is preferable to conducting more lower-power studies: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature. Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.

@@

Ethical review standards vary across instutitions and countries, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects. First, instructors may be concerned that ethics approval is not possible within the time constraints of the class. To mitigate this issue, we suggest contacting ethics bodies well in advance of classes to determine whether to create a standard protocol that encompasses all projects (as we did), or to set a timeline for students and instructors to submit individual study protocols very early in the course. Protocol development for both types -- umbrella and individual -- will be simplified if the study or pool of studies to be replicated is pre-selected by instructors. Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters. We recommend building training around ethical issues into the syllabus of replication-based classes. This practice is both positive for students and also mitigates potential ethics approval concerns.

@@

All reported results are from pre-registered, confirmatory analyses. In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).

@@

Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies. We coded projects independently on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), and then discussed our ratings and made adjustments (without coming to full consensus). The mean rating was `r round(mean(d$fidelity), digits = 2)` (range: `r round(min(d$fidelity), digits = 2)` -- `r round(max(d$fidelity), digits = 2)`). Several studies were essentially identical to the originals, but there was a group of others that included differences in population, number of trials, or method -- all factors that might plausibly have had an effect on the results.

@@

After data analysis, for each replication, the student carrying out each study and each instructor gave independent "replication ratings" to assess the subjective success of the replication. Our three-point rating system was based on the theoretical support for the original finding, "None" (no support; 0\%), "Partial" (some support; 50\%), and "Full" (replication consistent with original interpretation; 100\%). Student and instructor ratings were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.  The average rating given by instructors and students was `r 100 * round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)`\% and `r 100 * round(mean(d$replicated_student, na.rm=TRUE), digits = 2)`\% respectively.

@@

`r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value at $p < .05$. 
<!-- The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.  -->

@@

Our statistical findings mask a more optimistic message, however: In most of our projects, the next step for a motivated experimenter is clear. For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by altering the particular planned analysis or titrating the difficulty of the stimulus materials. In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample. And in some, differences of population would mean that followups would require further stimulus or task adaptation. More generally, we believe that our work here underscores the importance of iterated replication for pinpointing empirical effects and refining theories [see e.g., @lewis2016 for an example of this strategy and some discussion].
